### 2013-12-15 inst/doc/Advanced_writing_of_EML.Rmd

```{r}
dat <- read.csv(system.file("examples", "hf205-01-TPexp1.csv", package="reml"))
```

@@

```{r}
eml_write(eml, "hf205_from_reml.xml")
```

>>>>

```{r}
dat <- read.csv(system.file("examples", "hf205-01-TPexp1.csv", package="reml"), colClasses = 
                  c("factor", "Date", "Date", "Date", "factor", "factor", "factor"))
```

@@

```{r}
eml_write(eml, file="hf205_from_reml.xml")
```
